Can We Crunch the Social Graph on the Cheap?

### 2011-01-25 doc/hotpar2011/softxmt-hotpar2011.tex
comments

%% move stuff to defs file
\newcommand{\todo}[1]{{\bfseries [[#1]]}}
%% To disable, just uncomment this line
 \renewcommand{\todo}[1]{\relax}

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figures/multi-listwalk-totalconc-edited.pdf}
	\end{center}
	\caption{Throughput of listwalk versus total number of
          concurrent references offered by the cores. Data points for
          running 1 core are shown as circles, and data points for
          running 6 cores are shown as diamonds. 
%Notice that the throughput for a single core levels out at 10
%concurrent references. For 4 to 6 cores, the throughput levels off at
%around 36 references, which seems to be the most memory concurrency a
%processor can handle.
        }
	\label{fig:listwalk-totalconc}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/multi-green-edited.pdf}
  \end{center}
  \caption{Pointer chasing with coroutines, with one reference per
    coroutine. Number of coroutines per core is $\textit{total concurrent references} / \textit{number of cores}$.}
  \label{fig:multi-green}
\end{figure}

@@

\todo{do we want to include that the memory system imposes max limit so really more throughput is still achievable if there are enough ILP memory concurrency?}
\todo{also have results that remote cores over QPI plus delay 3us can make it up to the 175M, with sufficient number of coroutines}

>>>>

%% move stuff to defs file
\newcommand{\todo}[1]{{\bfseries [[#1]]}}
%% To disable, just uncomment this line
%% \renewcommand{\todo}[1]{\relax}

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.47\textwidth]{figures/multi-listwalk-totalconc-edited.pdf}
	\end{center}
	\caption{Throughput of listwalk versus total number of
          concurrent references offered by the cores. Data points for
          running 1 core are shown as circles, and data points for
          running 6 cores are shown as diamonds. 
%Notice that the throughput for a single core levels out at 10
%concurrent references. For 4 to 6 cores, the throughput levels off at
%around 36 references, which seems to be the most memory concurrency a
%processor can handle.
        }
	\label{fig:listwalk-totalconc}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.47\textwidth]{figures/multi-green-edited.pdf}
  \end{center}
  \caption{Pointer chasing with coroutines, with one reference per
    coroutine. Number of coroutines per core is $\textit{total concurrent references} / \textit{number of cores}$.}
  \label{fig:multi-green}
\end{figure}

@@

\todo{also have results that remote cores over QPI plus delay 3us can make it up to the 175M, with sufficient number of coroutines}
